Benchmark!!1

### 2020-12-28 paper/main.tex
explanation on Numba being not yet feature-complete

\section{Language-specific notes}
\subsection{Python}
Python does not allow to inline functions. Since using a flat matrix
requires to wrap matrix value lookup in a function, using a flat distance
matrix in Python is not beneficial. It would of course be possible to
inline by hand, i.e. formulate the correct 1-dimensional index in the
matrix for every lookup, but that would be impractical and defeat the
purposes and philosophy stated in Section~\ref{sec:intro}.
Running Python code that uses a flat representation with a JIT compiler
(e.g. Pypy, Numba) introduces automatic inlining and is likely to
remedy this.
\subsection{Julia}
Julia has native multi-dimensional arrays, which may be more efficient
than a flat representation. We will determine which version to use
based on experiment. Since Julia's arrays start with index 1, the code
for flat representation lookup of the distance between vertices $i$
and $j$ in matrix $d$ is \lstinline{d[i*n-n+j]}. It is worth noting
that it involves one subtraction on top of the addition and
multiplication used for 0-indexed languages.
\subsection{JavaScript}
All benchmarks are repetitive in nature, as they successively perform similar
operations with different input data. In JavaScript, when our
implementation loads 40 instances and performs the same
benchmarking operations on all 40 them, we observe a significant performance
hit after a few instances (2-5 times slower). In order to remedy this,
we re-start the program individually for each instance. Advanced
knowledge of this specific JavaScript engine might allow to remove that
performance hit, but this is clearly outside the scope of this
study. However it is worth noting that this can be a concern in general.

>>>>

\section{Language-specific notes}
\subsection{Python}
Python does not allow to inline functions. Since using a flat matrix
requires to wrap matrix value lookup in a function, using a flat distance
matrix in Python is not beneficial. It would of course be possible to
inline by hand, i.e. formulate the correct 1-dimensional index in the
matrix for every lookup, but that would be impractical and defeat the
purposes and philosophy stated in Section~\ref{sec:intro}.
Running Python code that uses a flat representation with a JIT compiler
(e.g. Pypy, Numba) introduces automatic inlining and is likely to
remedy this.
\subsection{Julia}
Julia has native multi-dimensional arrays, which may be more efficient
than a flat representation. We will determine which version to use
based on experiment. Since Julia's arrays start with index 1, the code
for flat representation lookup of the distance between vertices $i$
and $j$ in matrix $d$ is \lstinline{d[i*n-n+j]}. It is worth noting
that it involves one subtraction on top of the addition and
multiplication used for 0-indexed languages.
\subsection{JavaScript}
All benchmarks are repetitive in nature, as they successively perform similar
operations with different input data. In JavaScript, when our
implementation loads 40 instances and performs the same
benchmarking operations on all 40 them, we observe a significant performance
hit after a few instances (2-5 times slower). In order to remedy this,
we re-start the program individually for each instance. Advanced
knowledge of this specific JavaScript engine might allow to remove that
performance hit, but this is clearly outside the scope of this
study. However it is worth noting that this can be a concern in general.
\subsection{Numba}
Numba is not yet feature-complete for Numpy. A direct consequence is that some
benchmarks cannot be implemented for Numba. For example $np.insert()$ is not
implemented, but this function is needed for the $LN$
benchmark. Therefore the $LNS$ benchmark cannot be implemented with
Numba. Still, Numba is significant enough to be benchmarked and its
current performance are an indication of what to expect in years to come.
